%\section{Background}
\section{Problem Statement} 
The primary focus of this research is to detect glaucoma at an early stage. Glaucoma disease is a series of eye illnesses caused by damage to the optic nerve, which links the eye to the brain. If remain untreated, it can lead to blindness, it causes permanent loss of vision. This is the world's second leading cause of blindness. As per experiments, it is tracked down that the conclusion of the experts or ophthalmologists is abstract. This may cause a few misinterpretations when the glaucoma is distinguished as inaccurate, for example, false-positive and false-negative cases. Likewise, glaucoma is asymptomatic in the beginning phase. The harm advances gradually and it has no manifestations or early admonition signs until the vision is lost in the later stage. Additionally, if it tends to be distinguished in the beginning, the visual sight will be saved. It is shown that treatment and standard tests can forestall vision misfortune in individuals just at a beginning phase. On the other hand, if the vision loss has already occurred, the treatment can delay or hinder further loss of eyesight [6].

\vspace{5mm}
\noindent Here, mainly there are two different type of glaucoma such as- Primary Glaucoma also called chronic glaucoma which is caused by prolonged intraocular pressure inside the eyeball, whereas secondary glaucoma is caused by sudden events such as an injury to the eye or inflammation in the eye or the use of steroids. Open-angle glaucoma and closed-angle glaucoma are two types of glaucoma that can affect both primary and secondary glaucoma patients. Open-angle glaucoma is the most prevalent kind of glaucoma, accounting for 90\% of all cases [7]. There is a wide - open angle in between cornea and the iris in open-angle glaucoma. But in the case of closed-angle glaucoma, the angle is much narrower. Each of these subdivisions can be further divided into classes depending on conditions such as acute, intermittent, chronic, post status, etc. And there are other minor variants of glaucoma such as pigmentary glaucoma, exfoliation glaucoma, primary juvenile glaucoma, etc. In traditional cases, Ophthalmologists use Optical Coherence Tomography or OCT for detecting Glaucoma. For clinical imaging, Optical Coherence Tomography, or OCT, is commonly used. Optical sign known as OCT, procurement and preparation strategy that catches optic pictures in a three-dimensional picture. Both OCT and ophthalmologists are having a similar issue which is lacking and costly. They must be found in enormous emergency clinics or private emergency clinics. Some glaucoma patients are deficient assets. It might lead to people seeking late glaucoma therapy, which is bad for their eyesight. This requirement for specialists also a lot of costs are being constrained in terms of mass potential evaluating for faster discovery. For taking care of the issue of OCT pictures, fundus photos are chosen to be input pictures for this venture. A fundus camera is one more sort of camera that can be utilized to catch retina pictures. Fundus camera has more affordable costs contrasting and OCT pictures. It very well may be found in each region’s clinical focus, not just enormous clinics like OCT. Fundus pictures can be utilized for glaucoma finding through the CDR strategy [8].

\vspace{5mm}
\noindent Since glaucoma is such a prominent reason for blindness around the world, we must apply our knowledge of classification techniques to classify the various types of glaucoma for the betterment of the world. However, we are portraying and evaluating Convolutional Neural Organization (CNN) models for the discovery of glaucoma based on OCT Retinal Nerve Fiber Layer likelihood maps. Such CNN models can work in pairs with human specialists to keep up with large eye health and assist recognition of visual deficiency causing eye sickness [9]. We can easily use binary classifiers to differentiate between images of primary glaucoma and secondary glaucoma and then we can use another binary classifier to differentiate between images of open-angle glaucoma and closed-angle glaucoma. In this study, we are going to use Explainable AI (XAI) to classify scanned images of eyes that have glaucoma or have the chances to affect in future.

\nomenclature{$OCT$}{Optical Coherence Tomography}